---
title: "peptide-comparison"
output: html_document
---
May 23, 2022

Script to use MSStats to look at peptides from 2015 Oyster DIA proteomics. Compare peptide abundance between recently-settled oyster larvae held at 23C vs 29C. 

Script roughly follows:
Yaamini's MSStats script: https://github.com/RobertsLab/project-oyster-oa/blob/master/analyses/DNR_Skyline_20170524/2017-06-22-MSstats/2017-06-22-MSstats.R

MSstats manual (starting p44):http://msstats.org/wp-content/uploads/2017/01/MSstats_v3.7.3_manual.pdf
```{r}
sessionInfo()
```

```{r}
if (!require("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("MSstats")
```

```{r}
install.packages("dplyr")
```

```{r}
library(MSstats)
library(dplyr)
```


## Import Data

read in .csv of PeakAreas from 01-MSstats-Cgseed-DIA.R. In excel, I copy and pasted the peptide sequences into the ProteinName column. 
```{r}
PeakAreas <- read.csv("../data/20220611-PeakAreas.csv")
head(PeakAreas)
```

PeakAreas has 188508 obs and 15 variables



## Process Data
Add fraction column and have all cells listed as "1" from this google forum post: https://groups.google.com/forum/#!searchin/msstats/fractionations%7Csort:date/msstats/dVh6IEE0xTE/jiokWrNSCgAJ
```{r}
PeakAreas$Fraction <- "1"
PeakAreas
```

dataProcess function
```{r}
QuantData <- dataProcess(PeakAreas, normalization='equalizeMedians',
                         summaryMethod="TMP",
                         censoredInt="0",
                         MBimpute=TRUE,
                         maxQuantileforCensored=0.999)
```

 
count
<chr>
# of Protein	10219		
# of Peptides/Protein	1-1		
# of Transitions/Peptide	1-5




